countries & logical columns: dev'ing countries w/o China

### 2022-11-14 r-report/countries_deving_woc.Rmd
deving countries

---
title: "countries & logical columns: dev'ed countries"
output: pdf_document
date: "2022-10-24"
---

@@

data_base %>%
  filter(deved) %>%
  distinct(country,ISO,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>%
  kable("latex",booktabs = T, longtable = T)
```

>>>>

---
title: "countries & logical columns: dev'ing countries w/o China"
output: pdf_document
date: "2022-10-24"
---

@@

data_base %>%
  filter(deving_woc) %>%
  distinct(country,ISO,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>%
  kable("latex",booktabs = T, longtable = T)
```
